### 2019-03-18 README.Rmd
Download data if needed in README/vignette

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

@@

>>>>

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
knitr::opts_chunk$set(cache = TRUE)
```

@@

```{r getdata, include = FALSE}
if (!citesdb::cites_status()) citesdb::cites_db_download()
```
